\textbf{Proof Reconstruction in Classical Propositional Logic}

### 2017-04-26 slides/slides.tex
[ slides ] minor changes.

\newcommand{\gobackreconstruction}{
  \begin{tikzpicture}[overlay, remember picture, scale=0.5]
    \tikzset{shift={(current page.center)}, xshift=11.7cm,yshift=-8.4cm}
    \node[fill=plum,text=white, hyperlink node = reconstruction] (go) at (0,0) {\tiny Go Back};
  \end{tikzpicture}}

@@

\title[Proof Reconstruction in Classical Propositional Logic]
  {\textbf{Proof Reconstruction in Classical Propositional Logic}
}
\subtitle{(Work in Progress)}
\date{Agda Implementors’ Meeting XXV\\
May 9-15th}
\author[Jonathan Prieto-Cubides and Andr\'es Sicard-Ram\'irez]{Jonathan Prieto-Cubides
(Joint work with Andr\'es Sicard-Ram\'irez)}
\institute{
Universidad EAFIT\\
Medell\'in, Colombia}
% --------------------------------------------------------------------------

@@

>>>>

\newcommand{\gobackreconstruction}{
  \begin{tikzpicture}[overlay, remember picture, scale=0.5]
    \tikzset{shift={(current page.center)}, xshift=11.7cm,yshift=-8.4cm}
    \node[fill=plum,text=white, hyperlink node = after-reconstruction] (go) at (0,0) {\tiny Go Back};
  \end{tikzpicture}}

@@

\title[Proof Reconstruction in Classical Propositional Logic]
  {\textbf{Proof Reconstruction in Classical Propositional Logic}
}
\subtitle{(Work in Progress)}
\date{Agda Implementors’ Meeting XXV\\
May 9-15th}
\author[Jonathan Prieto-Cubides and Andr\'es Sicard-Ram\'irez]{Jonathan Prieto-Cubides\\
(Joint work with Andr\'es Sicard-Ram\'irez)}
\institute{
Universidad EAFIT\\
Medell\'in, Colombia}
% --------------------------------------------------------------------------

@@

\begin{frame}[fragile, label=after-reconstruction]
\end{frame}
